О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-09 pps-linear-bound/pps-linear-lower-bound.tex
Add definition of facher IPS

TODO: definition of facher IPS somewhere.

@@

\section{Constructing integral point sets}
For every integer $n\geq 3$ Solymosi~\cite{solymosi2003note} gives a construction of facher planar integral point set $M$
such as $|M| = n$ and for some $M_1, M_2 \in M$ holds $|M_1 - M_2| = 2$.
The construted set has both odd and even distances.

>>>>

@@

\section{Constructing integral point sets}

\begin{definition}
	A set $M\in\mathfrak{M}(2,n)$ is called \textit{facher}
	if $M$ consists of $n-1$ points on a straight line
	and one point out of the line.
\end{definition}

\begin{definition}
	A set $M\in\mathfrak{M}(m,n)$ is called \textit{optimal}
	if $\operatorname{diam}M=d(m,n)$.
\end{definition}

Facher sets are the simplest ones of planar integral point sets.
It is shown that for $9\leq n \leq 122$ all the optimal sets are facher~\cite{kurz2008minimum}.
For every cardinality $n$ (and every characteristic $q$~--- see~\cite{kurz2005characteristic} for details)
there exists a facher set $M\in\mathfrak{M}(2,n)$ (with the desired characteristic).

For every integer $n\geq 3$ Solymosi~\cite{solymosi2003note} gives a construction of facher planar integral point set $M$
such as $|M| = n$ and for some $M_1, M_2 \in M$ holds $|M_1 - M_2| = 2$.
The construted set has both odd and even distances.
